Free surface computations in mantle convection models

### 2016-04-22 free-surface-paper.tex
Change error symbol.

A better approach is to perform a finite element projection of the Stokes velocity 
solution onto the mesh velocity vector. Multiplying the boundary conditions 
(Equation~\eqref{eq:laplacian_bcs}) by a test function $\mathbf{w}$ and integrating over the free
surface part of the boundary, we find

@@

@@

This solution is only valid for infinitesimal topography. However, for small
initial topography $\zeta_0$ it seems to be sufficiently accurate to test convergence orders up 
to quadratic \citep{kramer2012implicit, furuichi2015implicit}.
We estimate the error by time-integrating the $L_2$ difference between the numerical and analytical
solutions at the center point of the free surface:
\begin{equation}
\mathrm{Error} = \frac{1}{4\tau}\int_0^{4 \tau} \lVert \zeta_\mathrm{numeric}(L/2, t) - \zeta_\mathrm{analytic}(L/2, t) \rVert_2 \text{ d}t.
\end{equation}

@@

>>>>

A better approach is to perform an $L_2$ projection of the normal velocity $\mathbf{u}\cdot\mathbf{n}$
onto the free surface $\Gamma_F$. Multiplying the boundary conditions 
(Equation~\eqref{eq:laplacian_bcs}) by a test function $\mathbf{w}$ and integrating over the free
surface part of the boundary, we find

@@

\subsection{Relaxation of sinusoidal topography}
\label{sec:topography_relaxation}

@@

This solution is only valid for infinitesimal topography. However, for small
initial topography $\zeta_0$ it seems to be sufficiently accurate to test convergence orders up 
to quadratic \citep{kramer2012implicit, furuichi2015implicit}.
We estimate the error $E$ by time-integrating the $L_2$ difference between the numerical and analytical
solutions at the center point of the free surface:
\begin{equation}
E = \frac{1}{4\tau}\int_0^{4 \tau} \lVert \zeta_\mathrm{numeric}(L/2, t) - \zeta_\mathrm{analytic}(L/2, t) \rVert_2 \text{ d}t.
\end{equation}

@@

\subsection{Mesh adaptivity}
\label{sec:mesh_adaptivity}
